\section{Board}
\label{board}

\subsection{Selection of the Board Chair}
\label{selection-of-the-board-chair}

\begin{enumerate}
 \item
  The Board must select an individual who shall serve as its Chair for the whole term of the National Executive, to preside over its meetings.
 \item
  The Board Chair must be a member of a member society at the time of appointment.
 \item
  This individual shall be put forward for confirmation for a term spanning the remainder of the fiscal year at the General Assembly held at Summit on Development of Engineering Societies.
\end{enumerate}

\subsection{The Vice-Chair}
\label{the-vice-chair}

\begin{enumerate}
 \item
  The Board must also designate one of its members as Vice-Chair, who is to fulfill the duties of the Chair in their absence.
 \item
  The President shall not be eligible to fill the position of Vice-Chair.
\end{enumerate}

\subsection{Responsibilities of the Board Chair}
\label{responsibilities-of-the-board-chair}

\begin{enumerate}
 \item
  The Board Chair is responsible for calling meetings in accordance with the Constitution, distributing Board meeting minutes to the Board for approval, and submitting approved minutes to be posted on the website.
 \item
  In addition to responsibilities to the Board, the Board Chair also chairs the General Assembly. As a part of chairing the General Assembly, the Board Chair is responsible for the following:
  \begin{enumerate}
   \item
    Ensuring, in conjunction with the relevant Activity Manager, that sufficient time and resources are scheduled to complete all proceedings
   \item
    Ensuring that members are made aware of the meetings as required by the Constitution
   \item
    Ensuring that members are adequately prepared for the meeting by providing them with previous meeting minutes, and other relevant documents
   \item
    Ensuring that a process exists for members to submit proposals and counter-proposals
   \item
    Ensuring that a preliminary agenda is circulated as required for each meeting of the General Assembly

  \end{enumerate}
 \item
  In the absence of the Board Chair, the duties above, and otherwise assigned to the Board Chair, are completed by the Vice-Chair.

\end{enumerate}

\subsection{Meetings}
\label{meetings}

\subsubsection{Regular Meetings}
\label{regular-meetings}

\begin{enumerate}
 \item
  Board Meetings shall be held at any time and place to be determined by the Board, provided that five (5) days verbal or written notice of such meeting shall be given to each Board member.
 \item
  There shall be at least six (6) Board Meetings per year.
 \item
  Each Board Member present at the meeting is authorized to exercise one (1) vote.
 \item
  If all the Board of the Federation consent, one or more Board Members may participate in a Board Meeting by means of a technological communication method, such as the telephone, allowing all persons participating in the meeting to hear each other.
 \item
  Board Members participating in such a meeting by such means are deemed to be present at the meeting.
 \item
  Voting by proxy is prohibited for Board Members.
\end{enumerate}

\subsubsection{Emergency Meetings}
\label{emergency-meetings}

\begin{enumerate}
 \item
  Emergency meetings of the Board may be called for urgent or special purposes requiring immediate action, provided two thirds of the members of the Board agree to call the meeting.
\end{enumerate}

\subsubsection{Quorum}
\label{quorum}

\begin{enumerate}
 \item
  For there to be a quorum at a meeting of the Board, two-thirds (2/3) of the Board must be present.
\end{enumerate}

\subsection{Electronic Voting}
\label{electronic-voting}

\begin{enumerate}
 \item
  A resolution may be taken by the Board via electronic methods if all Board Members entitled to vote on that resolution at a meeting of directors, vote in favour.
 \item
  The resolution is as valid as if it has been passed at a meeting of the Board Meeting.
\end{enumerate}

\subsection{Powers of Appointment}
\label{powers-of-appointment}

\subsubsection{Committees}
\label{committees}

\begin{enumerate}
 \item
  The Board may appoint committees whose members will hold their offices at the will of the Board.
\end{enumerate}

\subsubsection{Agents and Employees}
\label{agents-and-employees}

\begin{enumerate}
 \item
  The Board may appoint agents and engage employees as it seems necessary from time to time and such persons shall have the authority and shall perform duties as prescribed by the Board at the time of appointment.
 \item
  A reasonable remuneration for all employees of the Federation shall be fixed by resolution of the Board as allowed by the budget.
\end{enumerate}

\subsection{Powers of Administration}
\label{powers-of-administration}

\begin{enumerate}
 \item
  The Board may administer the affairs of the Federation in all things and make or cause to be made for the Federation, in its name, any kind of contract which the Federation may lawfully enter into and, save as hereinafter provided, generally, may exercise all such other powers and do all such other acts and matters of the Federation is by its by-laws or otherwise authorized to exercise and do.
\end{enumerate}

\subsection{Remuneration}
\label{remuneration}

\begin{enumerate}
 \item
  The Board shall serve without remuneration and no Board Member shall directly or indirectly receive any profit from holding the position, provided that reasonable expenses incurred in the exercise of the Board Member's duties are reimbursed.
\end{enumerate}

\subsection{EDBA Training}
\label{edba-training}

\begin{enumerate}
 \item
  Each year, the Board shall undergo certified EDBA-related training by August 1st.
 \item
  This training shall be organized by the National Councillors and given by an external facilitator.
 \item
  The following topics, at minimum, must be covered by this training or these trainings:
  \begin{enumerate}
   \item
    Ableism, Intellectual and Physical
   \item
    Classism
   \item
    Consent
   \item
    Drinking Culture
   \item
    Gender and Sexual Diversity
   \item
    Multiculturalism, including Culture and Religion
   \item
    Racism
   \item
    Truth and Reconciliation
   \item
    The effects of Intersectionality between the above topics.
   \item
    Psychological First Aid
  \end{enumerate}

\end{enumerate}

\subsection{Vacancy}
\label{vacancy}

\begin{enumerate}
 \item
  The office of a Board Member shall be automatically vacated upon the occurrence of a resignation, invalidity or death.
 \item
  An outgoing Board Member or Commissioner shall remain in office until its vacancy is presented to the Board.
\end{enumerate}
