\section{General Meetings}
\label{general-meetings}

\subsection{Annual General Meeting}
\label{annual-general-meeting}

\begin{enumerate}
 \item
  The Annual General Meeting (AGM) of the Federation takes place at CELC in January each year.
 \item
  This General Assembly consists of at least two sessions, with at least one day between the sessions for counter-proposal writing.
 \item
  The AGM gives members the opportunity to participate in the organizational decision-making process.
 \item
  It is chaired by the Board Chair and moderated based on the most recent edition of Robert's Rules of Order Newly Revised (RRoONR).
 \item
  To participate in these meetings, members are required to provide to the Board Chair a current and original proxy, delegating their voting rights to an individual or another member, a minimum of one week in advance of a General Assembly.
\end{enumerate}

\subsection{Summit on Development of Engineering Societies}
\label{summit-on-development-of-engineering-societies}

\begin{enumerate}
 \item
  Summit on Development of Engineering Societies (SDES) is a gathering of members and the Board to discuss the affairs of the Federation, collaborate, and network.
 \item
  Summit on Development of Engineering Societies takes place in late September, or early October, and the host is elected at the CELC of the preceding calendar year.
\end{enumerate}

\subsection{Canadian Engineering Spring Summit}
\label{canadian-engineering-spring-summit}

\begin{enumerate}
 \item
  Canadian Engineering Spring Summit (CESS) is an online gathering of members and the Board to discuss the affairs of the Federation, collaborate, and network.
 \item
  Canadian Engineering Spring Summit takes place in March.
\end{enumerate}

\subsection{Bootcamp (Non-General-Meeting)}
\label{bootcamp-non-general-meeting}

\begin{enumerate}
 \item
  Bootcamp is an online gathering of members and the Board whose purpose is to host training sessions and discussions, along with networking.
 \item
  Bootcamp will not host a General Assembly and will be one day in length.
 \item
  Bootcamp takes place in June, or July.
\end{enumerate}

\subsection{Online Seasonal Update Meetings (O-SUMs)}
\label{online-seasonal-update-meetings-o-sums}

\begin{enumerate}
 \item
  The CFES will hold two Remote General Meetings to bridge the gap between in person General Meetings.
 \item
  These meetings are an online gathering of Members and the Board.
 \item
  The focus of these meetings are for the Board and Activity Managers to give updates to the Membership on progress on their portfolios, projects and advocacy work.
 \item
  These meetings will also include opportunities for Membership feedback.
 \item
  These 2 meetings will not host a General Assembly and be scheduled for approximately 2-3 hours with one taking place in July and another in November.
 \item
  Organization of these meetings and agendas are the responsibility of the Board Chair with support from relevant members of the Board.
\end{enumerate}

\subsection{Meeting Guidelines}
\label{meeting-guidelines}

\subsubsection{Calling a Meeting}
\label{calling-a-meeting}

\begin{enumerate}
 \item
  A General Assembly shall be called on resolution of the Board or on a written requisition of no less than one quarter (1/4) of the active members.
\end{enumerate}

\subsubsection{Live Translation}
\label{live-translation}

\begin{enumerate}
 \item
  At every general assembly, simultaneous translation services must be available, whether they be professionally outsourced or member-led.
 \item
  If outsourced, these will be provided at a cost to the organizing committee at which the general assembly takes place.
\end{enumerate}

\subsubsection{Meeting Agenda}
\label{meeting-agenda}

\begin{enumerate}
 \item
  At every annual general assembly, in addition to any other business that may be transacted, the report of the Board, the financial statement and the report of the auditors shall be presented.
\end{enumerate}

\subsubsection{Notice of a meeting}
\label{notice-of-a-meeting}

\begin{enumerate}
 \item
  A thirty (30) day written notice shall be given to each member of any General Assembly.
 \item
  Notice of any meeting where special business will be dealt with should contain sufficient information to permit the member to form a reasoned judgement on the decision to be taken.
 \item
  No error or omission in giving notice of any members assembly or any adjourned members assembly of the Federation shall invalidate such meeting or make void any proceedings taken thereat, and any member may at any time waive notice of any such meeting and may ratify, approve and confirm any or all proceedings taken or had thereat.
 \item
  For purpose of sending notice to any member Board Member for any meeting or otherwise, the address of the member or Board Member shall be that persons last address recorded on the books of the Federation.
\end{enumerate}

\subsubsection{Voting and Quorum}
\label{voting-and-quorum}

\begin{enumerate}
 \item
  All active members shall have only one (1) vote.
 \item
  All questions before the General Assembly shall be determined by a majority of votes of members present and voting unless otherwise specifically provided by resolutions or mentioned in this constitution.
 \item
  Two thirds (2/3) of the active members shall constitute quorum at a General Meeting.
\end{enumerate}

\subsubsection{Speaking Rights}
\label{speaking-rights}

\begin{enumerate}
 \item
  Active members, Regional Ambassadors, National Councillors, and National Executive have speaking rights during the assembly.
\end{enumerate}

\subsubsection{Order}
\label{order}

\begin{enumerate}
 \item
  At all assemblies of the Federation, the chair must apply the rules of deliberating assemblies as outlined in the Robert's Rules of Order, except where contrary dispositions are adopted by the Federation.
 \item
  The Board Chair shall preside over the meetings of the General Assembly.
 \item
  At a General Assembly the National Executive and each individual Board Member has the right to propose motions with no need of a seconder.
\end{enumerate}

\subsubsection{Proxy}
\label{proxy}

\begin{enumerate}
 \item
  A member may, by means of verifiable communication by its President, either original, facsimile, or electronic, appoint a proxy holder to attend and act at a specific meeting of the General Assembly.
 \item
  Notice of each meeting of the General Assembly must remind the members of their ability to appoint a proxy holder.
 \item
  All proxy votes must be deferred to a member of the active member deferring or to another active member of the CFES.
\end{enumerate}

\subsubsection{Minutes}
\label{minutes}

\begin{enumerate}
 \item
  Minutes shall be taken in both English and French at all meetings of the General Assembly.
 \item
  The full and proper text of the minutes shall be distributed to all members in both English and French within thirty days of the adjournment of the meeting.
\end{enumerate}

\subsection{Mail-In Ballot}
\label{mail-in-ballot}

\subsubsection{Ineligible Items}
\label{ineligible-items}

\begin{enumerate}
 \item
  The following items may not be passed using a mail-in ballot;
\begin{enumerate}
 \item
  Constitutional Amendments
 \item
  Rescinding of motions
\end{enumerate}
\end{enumerate}


\subsubsection{Procedure}
\label{procedure}

\begin{enumerate}
 \item
  Ballots submission by mail or any official communication (assuming confidentiality requirements are met as set forward by the National Executive), hereby referred to as a ``mail-in ballot'', is valid for the General Assembly or the Board except in the case where Canadian non-profit law prohibits such action.
 \item
  The Board shall call a mail-in ballot on written requisition of no less than one quarter (1/4) of the active members.
 \item
  A mail-in ballot shall be subject to the same guidelines and regulations as an Annual General Meeting, whether it be to clarify quorum or the outcome of the proposition.
 \item
  The Board will determine any additional rules.
 \item
  To be valid, mail-in ballots must be returned to the Federation within thirty (30) days following the mailing of the voting notice to all the active members.
 \item
  The Board has, between the thirty-fifth (35th) and the fiftieth (50th) day following the mailing of the voting notice, to send to all the members and directors the results of the mail-in ballot.
 \item
  Any error or omission in mailing the voting notice of the mail-in ballot will not annul the ballot.
 \item
  The active members will receive the voting notice at their last known address in the books of the Federation.
 \item
  All motions passed through a mail in ballot are subject to ratification at the next meeting of the General Assembly.
\end{enumerate}

\subsection{Pre-General Meeting Videos}
\label{pre-general-meeting-videos}

\begin{enumerate}
 \item
  The National Executive shall create videos prior to every conference that involves a General Assembly Session to ensure members are informed about relevant topics to the conference; including but not limited to the policies being discussed and ongoing mandates.
 \item
  The total duration of these videos shall not exceed 30 minutes, and videos must be provided a minimum of 1 week before the conference begins.
\end{enumerate}
