\section{Board}\label{board}

\subsection{Tasks and
 Responsibilities}\label{tasks-and-responsibilities}

\begin{enumerate}
 \item
  The Board' tasks and responsibilities include, but are not limited to:
\end{enumerate}

\begin{enumerate}
 \item
  Oversight of CFES finances and administration
 \item
  Establishing an agenda in advance of all meetings
 \item
  Determining electoral procedures as needed
 \item
  Allocating, at Spring Meeting, the funds from the travel fund to each major meeting of the CFES during the fiscal year. Such meetings include:

  \begin{enumerate}
   \item
    Summer Meeting
   \item
    Summit on Development of Engineering Societies
   \item
    Fall Meeting
   \item
    CELC
   \item
    Spring Meeting
  \end{enumerate}
\end{enumerate}

\begin{enumerate}
 \item
  Tracking progress of the CFES Team
\end{enumerate}

\begin{enumerate}
 \setcounter{enumi}{4}
 \item
  Hearing any appeals from the Incident Response Committee
\end{enumerate}

\subsection{Board Member Conduct}\label{board-member-conduct}

\subsubsection{Conduct}\label{conduct}

\begin{enumerate}
 \item
  Board Members shall act honestly and in good faith in the best interests of the Federation as a whole, and exercise the care, diligence and skill of a reasonably prudent person in carrying out their duties.
 \item
  To ensure Board Members act in this way, the Board is to approve, no later than June 1st of each year, a Code of Conduct which will, at minimum, cover the following topics:
\end{enumerate}

\begin{enumerate}
 \item
  Conflict of Interest, in accordance with the statements below
 \item
  Culture
 \item
  Responsibilities
 \item
  Confidentiality

  \begin{enumerate}
   \item
    Board Members must sign the Code of Conduct approved by the Board no later than June 15th of the year in which they hold office, and the signed copy is to be stored in the organization's records.
  \end{enumerate}
\end{enumerate}

\subsubsection{Conflict of Interest for Board
 Members}\label{conflict-of-interest-for-board-members}

\begin{enumerate}
 \item
  No Board Member may, in their role as a Board Member, participate in any decision, exercise an official power or perform an official duty or function in which they may have either a conflict of interest or an apparent conflict of interest.
 \item
  Such circumstances may include, but are not limited to, the following:
\end{enumerate}

\begin{enumerate}
 \item
  Matters from which a Board Member stands to benefit personally
 \item
  Matters involving a member society of the Federation of which a Board Member is themselves a member

  \begin{enumerate}
   \item
    Directors are expected to declare any situation in which they have a conflict of interest, whether real or perceived.
   \item
    In the event a Board Member believes another Board Member has a conflict of interest, the matter shall be brought to the Board Chair for a decision.
   \item
    The Board may overturn the decision of the Board Chair by majority vote.
   \item
    In the event of a conflict of interest for the Board Chair, the Board Chair shall relinquish the chair to the Vice-Chair of the Board until the matter is resolved.
  \end{enumerate}
\end{enumerate}

\subsection{Closed Sessions}\label{closed-sessions}

\begin{enumerate}
 \item
  The Board may, from time-to-time, meet in closed session to discuss matters of a confidential nature.
 \item
  Persons eligible to participate in a closed session are the Board, as well as any other individuals included by a resolution requiring a two-thirds (2/3) majority.
 \item
  Matters eligible for discussion in closed session are limited to:
\end{enumerate}

\begin{enumerate}
 \item
  Contractual negotiations
 \item
  Personnel concerns
 \item
  Matters which pose a reputational risk to the Federation

  \begin{enumerate}
   \item
    To move to a closed session, the Board must pass a resolution to do so by a two-thirds (2/3) majority.
   \item
    No resolutions may be passed once the Board has entered a closed session, other than motions to remain in the closed session, which also require a two-thirds (2/3) majority.
   \item
    Persons privy to closed session discussions are required to keep such matters confidential.
   \item
    In addition to those present, only members of the Board not present at a given closed session are entitled to be informed of the content of discussion after the fact.
   \item
    Such information shall only be provided by the Board Chair to the member or members unable to attend.
  \end{enumerate}
\end{enumerate}

\subsection{Written Resolution}\label{written-resolution}

\begin{enumerate}
 \item
  In addition to the provisions surrounding written resolutions contained in the Constitution, Board Members shall return to the Board Chair their vote on any written resolution within three (3) business days.
 \item
  Written resolutions may be carried out by electronic means that the Board Chair determines to be secure.
 \item
  The results of a written resolution must be announced by the Board Chair at the next meeting.
\end{enumerate}

