\section{Commissioners}\label{commissioners}

\subsection{Commissioner Overview}\label{commissioner-overview}

\begin{enumerate}
 \item
  Commissioners are appointed, as required, by the National Executive to assist in the completion of National Executive duties and organizational goals.
 \item
  The list of potential Commissioner positions as well as duties can be found is the reference document ``{[}EN{]} Reference Document - Commissioners''
 \item
  The following positions are normally filled; however, Commissioner positions may be created by the National Executive and approved by the Board or left vacant at the discretion of the National Executive.
 \item
  In the event of a vacancy in the following Commissioner positions, the responsible National Executive will accept the assigned tasks and responsibilities.
 \item
  The Commissioners are:

  \begin{enumerate}
   \item
    Governance Commissioner
   \item
    Corporate Relations Commissioner
   \item
    Information Technology Commissioner
   \item
    International Relations Commissioner
   \item
    Leadership Development Commissioner
   \item
    Media \& Marketing Commissioner
   \item
    Bilingualism Commissioner
   \item
    Data Commissioner
   \item
    Logistics Commissioner
  \end{enumerate}

 \item
  The Commissioners' general responsibilities include:

  \begin{enumerate}
   \item
    Completing tasks assigned to them by the National Executive
   \item
    Contributing to CFES communications
   \item
    Acting as advisor and consultant to members as appropriate
   \item
    Creating a summary transition document for each position by April 30th to be stored in the electronic CFES archive
   \item
    Providing written updates on tasks completed at a frequency determined by the National Executive and at minimum every two months
  \end{enumerate}
\end{enumerate}

\subsection{Eligibility}\label{eligibility}

\begin{enumerate}
 \item
  To be eligible for a Commissioner position, the applicants must be a member of an active member at the time of candidature, while also fulfilling any additional requirements outlined by the relevant Commissioner portfolio and the National Executive.
 \item
  Additional requirements may change from year to year, and have included stipulations such as being present at the Annual General Meeting.
 \item
  No student shall hold more than one position within the CFES Team at any given time.
\end{enumerate}

\subsection{Applications}\label{applications}

\begin{enumerate}
 \item
  Persons interested in a Commissioner position must declare their intentions by completing and submitting an application to the National Executive.
 \item
  This application form will be made available to all eligible candidates and the deadline for submission will be decided by the National Executive.
\end{enumerate}

\subsection{Selection}\label{selection}

\begin{enumerate}
 \item
  The incoming National Executive will decide on a method of selection which at minimum must include an application phase.
 \item
  The selected applicants will be put forth to the Board for ratification.
\end{enumerate}

\subsection{Corporate Relations
 Commissioner}\label{corporate-relations-commissioner}

\begin{enumerate}
 \item
  The Corporate Relations Commissioner is responsible for the centralized funding and partnership activities of the CFES.
 \item
  This Commissioner reports directly to the VPE.
 \item
  The Corporate Relations Commissioner's tasks and responsibilities include the following:

  \begin{enumerate}
   \item
    Ensure the compliance and maintenance of the Federation relationships with Partnership Agreements
   \item
    Provide support for Activity Managers and their VP Sponsorships with their respective sponsorship initiatives
   \item
    Seeking additional Federation partnerships or funding opportunities to bring to the Board and the Activity Managers for approval
   \item
    Compiling and presenting all active funding partnerships to the members at the Annual General Meeting
   \item
    Maintain and update the CFES Sponsor Database, which includes contact information of the past activity, sponsors, and sponsorship packages and make it available to the Activity Managers
  \end{enumerate}
\end{enumerate}

\subsection{Governance Commissioner}\label{governance-commissioner}

\begin{enumerate}
 \item
  The Governance Commissioner is responsible for the general record-keeping of the CFES.
 \item
  This Commissioner reports directly to the VPFA.
 \item
  The Governance Commissioner's tasks and responsibilities include:

  \begin{enumerate}
   \item
    Document control of financial statements and records in accordance with laws applicable to the CFES.
   \item
    Ensuring the list of members prepared by the VPFA each year is up-to-date.
   \item
    Taking minutes for CFES General Assemblies and assigning minute takers for CFES General Assemblies where they are not present
   \item
    Collating the minutes after the assemblies, and ensuring their publication on the CFES website.
   \item
    In conjunction with the meeting minutes, a continual document be distributed to the members that outlines the pertinent information regarding assemblies; including the motion name, motion number, spirit of the motion, and whether or not the motion passes, failed, or was tabled to a certain time.
   \item
    Updating the CFES Acronym Cheat Sheet and ensuring it is an accessible resource to all members.
   \item
    Taking the minutes of Board meetings.
   \item
    Ensuring the most updated versions of all legal and financial documents are shared with the Board
  \end{enumerate}
\end{enumerate}

\subsection{Information Technology
 Commissioner}\label{information-technology-commissioner}

\begin{enumerate}
 \item
  The Information Technology (IT) Commissioner will maintain and administer all aspects of the electronic infrastructure of CFES.
 \item
  This Commissioner reports directly to the VPFA.
 \item
  The Information Technology Commissioner's tasks and responsibilities include:

  \begin{enumerate}
   \item
    Maintaining access to the CFES website, email accounts, electronic mailing list, and the electronic CFES Archive
   \item
    Assisting with the creation of activity, service, and program websites.
   \item
    Maintaining the security of the electronic infrastructure of the CFES.
   \item
    Maintaining the CFES electronic file storage system.
   \item
    Maintaining the availability of the CFES website.
   \item
    Providing members of the CFES information with respect to proper IT practices
   \item
    Supporting Activities with email accounts for the Organizing Committee and subdomain connections
  \end{enumerate}
\end{enumerate}

\subsection{Bilingualism Commissioner}\label{bilingualism-commissioner}

\begin{enumerate}
 \item
  The Bilingualism Commissioner is responsible for ensuring that CFES operations are bilingual.
 \item
  The Bilingualism Commissioner's tasks and responsibilities include:

  \begin{enumerate}
   \item
    Coordinating all text translation services for the Board, the National Executive and Commissioners, including the organization of any translators that may be contracted by the CFES
   \item
    Ensuring translations of bilingual documents are updated within 60 days of any changes
   \item
    Serving as a contact point for members' language concerns
   \item
    Implementing activities and/or initiatives to promote mutual understanding between members
   \item
    Promoting bilingualism within CFES by raising awareness of both official languages and relevant language issues through a working group on bilingualism
   \item
    Working with activity, service and program organizers to manage translation services, as necessary
  \end{enumerate}
\end{enumerate}

\subsection{Media \& Marketing
 Commissioner}\label{media-marketing-commissioner}

\begin{enumerate}
 \item
  The Media \& Marketing Commissioner is responsible for the CFES brand, and supporting the CFES Team through layout and design activities.
 \item
  The Media \& Marketing Commissioner reports directly to the VPC.
 \item
  The Media \& Marketing Commissioner's tasks and responsibilities include:

  \begin{enumerate}
   \item
    Maintenance and upkeep of an archive of original files relating to the logo, banners, branded items, and templates.
   \item
    Maintenance and upkeep of the design of the CFES website.
   \item
    Maintenance and upkeep of the content of the CFES website, which includes ensuring that the latest available information on CFES events is easily accessible on the website such as the date of the event and the host school.

    \begin{enumerate}
     \item
      This information must be updated at most three weeks after a General Assembly where an Activity Manager has been ratified.
    \end{enumerate}
   \item
    Maintenance and enforcement of logo and branding guidelines of the CFES
   \item
    Assisting activities, programs and services with the creation of design templates for documents or promotional materials, as necessary
   \item
    Sourcing quotes for branded items for the CFES or Activity Managers as necessary
   \item
    Updating social media profiles for the Federation
   \item
    Acquiring business cards for the Board with the official logo, individual position, and contact information by Summer Meeting
  \end{enumerate}
\end{enumerate}

\subsection{Leadership Development
 Commissioner}\label{leadership-development-commissioner}

\begin{enumerate}
 \item
  The Leadership Development Commissioner is responsible for organizing material related to leadership and interpersonal skills and preparing this material to distribute to the members.
 \item
  This position reports directly to the VPS.
 \item
  The Leadership Development Commissioner's tasks and responsibilities include:

  \begin{enumerate}
   \item
    Preparing a series of sessions for CFES related to the development of leadership and interpersonal skills in conferences.
   \item
    Communicating with both the Board and the National Executive to ensure that the Leadership Development curriculum is aligned with the goals and mission of the CFES.
   \item
    Communicating with CFES Activity Managers to arrange leadership sessions if needed.
   \item
    Communicating with the CELC Activity Manager to arrange space and required materials to facilitate sessions.
   \item
    Ensuring that any persons required to run a Leadership Development session are available to run the required sessions at CFES CELC.
   \item
    Make digitally available to members the material presented at CFES CELC under the Leadership Development portfolio.
   \item
    Develop and make digitally available leadership development materials for use by members at their respective institutions.
  \end{enumerate}
\end{enumerate}

\subsection{Data Commissioner}\label{data-commissioner}

\begin{enumerate}
 \item
  The Data Commissioner is responsible for the advocacy efforts of the CFES through the development, execution, and interpretation of the National Survey.
 \item
  This position reports to the VPA.
 \item
  They work closely with the VP Academic, serve as a liaison between the various Working Groups and the CFES executive, and publish reports and documentation on the development and results of the National Survey.
 \item
  The Data Commissioner's tasks and responsibilities include:

  \begin{enumerate}
   \item
    Maintain the yearly National Survey
   \item
    Ensure uniform and standardized collection of data
   \item
    Distribute the National Survey and advertise it in collaboration with the VPC
   \item
    Collect data and share relevant analysis
   \item
    Generate a report from the collected combined National Survey data
   \item
    Research, compile, and document similar processes across member schools and organizations
   \item
    Act as a resource for the Board and member schools pertaining to the uniformity of activities and operations across other member schools and organizations
   \item
    Ensure all data and surveys is adhering to ethical standards of collection, and participate in any required training to do so
   \item
    Ensure the data from the national survey is backed up in a secondary location attached to vpa@cfes.ca
  \end{enumerate}
\end{enumerate}

\subsection{Logistics Commissioner}\label{logistics-commissioner}

\begin{enumerate}
 \item
  The Logistics commissioner is responsible for organizing and researching material related to the conferences under the services portfolio and supporting the VPS as needed while keeping an open line of communication with the Activity Managers for updates.
 \item
  The Logistics Commissioners' tasks and responsibilities include:

  \begin{enumerate}
   \item
    Lead the Logistics working group alongside the VPS.
   \item
    Help encourage member societies to bid and host CFES Activities and promote them.
   \item
    Maintenance and upkeep of an archive of original files relating to conferences and bids.
   \item
    Assisting with the management of conferences by attending check-in meetings and reviewing OC documentation.
   \item
    Communicating with an assigned Activity Manager to get organizational updates.
   \item
    Act as an additional CFES resource for the activity manager.
   \item
    Develop and make digitally available Services best practices and guideline documents.
  \end{enumerate}
\end{enumerate}

