\section{Internal Meetings}\label{internal-meetings}

\subsection{Purpose}\label{purpose}

\begin{enumerate}
 \item
  CFES holds four internal meetings a year for the CFES Team, with the aim of coordinating Federation initiatives, strategy, goals and the transition process.
\end{enumerate}

\subsection{Online Meetings}\label{online-meetings}

\subsubsection{Attendance}\label{attendance}

\begin{enumerate}
 \item
  All members of the Board members, Commissioners, and Activity Managers are expected to attend.
 \item
  Working group members are invited to attend.
\end{enumerate}

\subsubsection{Summer Meeting}\label{summer-meeting}

\begin{enumerate}
 \item
  Focus on group initiatives, with a review of action/strategic plan progress.
 \item
  Serves as the planning session for the Summit on Development of Engineering Societies.
 \item
  It is traditionally held in late June or July, and spans from a Friday to a Sunday.
\end{enumerate}

\subsubsection{Fall Meeting}\label{fall-meeting}

\begin{enumerate}
 \item
  Continued work on group initiatives, with further review of action strategic plan progress.
 \item
  Serves as the planning session for CELC.
 \item
  It is traditionally held in late October or early November, and spans from a Friday to a Sunday.
\end{enumerate}

\subsection{In-Person/Hybrid Meetings}\label{in-personhybrid-meetings}

\subsubsection{Attendance}\label{attendance-1}

\begin{enumerate}
 \item
  Only members of the Board may attend with the following exceptions:

  \begin{enumerate}
   \item
    The Incoming and Outgoing Corporate Relations Commissioners may attend Spring Meeting.
   \item
    Activity Managers may attend Spring Meeting as per the Activity Agreement
  \end{enumerate}
 \item
  Exceptions can be made by the Board to allow Commissioners or Activity Managers to attend

  \begin{enumerate}
   \item
    The respective Vice President overseeing the Commissioner or Activity Manager must provide a letter to the Board detailing the tasks the individual will complete at the In-Person Meeting and why they must attend.
   \item
    These letters will be discussed and voted on at the Board meeting after the submission of the letter and require a majority vote to approve the individual's attendance.
  \end{enumerate}
 \item
  These meetings shall be accessible online for members of the Board who are unable to attend in-person and any Commissioner/Activity Manager who wishes to attend.
\end{enumerate}

\subsubsection{Spring Meeting}\label{spring-meeting}

\begin{enumerate}
 \item
  Transition meeting; time is given for individual and group transitions.
 \item
  Initiatives from the prior year are transitioned to the new team, and the action planning process is begun.
 \item
  It is traditionally held in mid-to-late March, and spans from a Thursday to a Sunday, with the Friday spent with Engineers Canada.
\end{enumerate}

\subsubsection{CELC Pre-Week}\label{celc-pre-week}

\begin{enumerate}
 \item
  Drive completion of group initiatives and action plan for progress against strategic plan.
 \item
  Familiarize oneself with the Activity's venue and meet the Activity OC.
 \item
  Finalize CELC member representative stream and begin planning for transitioning.
 \item
  This week is not in place for the Board, including the VP Services, to conduct responsibilities of the Activity Manager and the Activity OC outlined in their respective activity agreement.
 \item
  Pre-week is recommended to be held on the following timeline, respecting the competing needs of the holiday season and a busy CELC agenda:
\end{enumerate}

\begin{enumerate}
 \item
  If CELC begins on January 2, it is held from December 30 through January 2;
 \item
  If CELC begins on January 3, it is held from Dec 31 through January 3;
 \item
  And if CELC begins on January 4 or later, CELC Pre-Week is to begin 3 days before CELC itself.

  \begin{enumerate}
   \item
    It is up to the Board, with consultation with the current CFES VPS and CELC Activity Manager, to reduce or increase the duration of pre-week based on the amount of outstanding items to be finalized.
   \item
    The CELC Activity Manager shall be informed of the final decision on the duration of pre-week no later than 1 week after the SDES held prior to the CELC conference.
  \end{enumerate}
\end{enumerate}

\subsection{Logistics}\label{logistics}

\begin{enumerate}
 \item
  These meetings are organized by the National Executive.
 \item
  The CFES main budget shall be allocated to cover accommodations, food, and logistics of CFES Spring Meeting, Summer Meeting, and Fall Meeting.
 \item
  It shall also be allocated to cover food and logistics for CELC Pre-Week, while accommodations will be covered by the CELC Activity Manager's budget.
 \item
  In addition, the National Executive holds an Executive Transition Meeting for the National Executive and the individuals who have been elected to the National Executive for the following year.
 \item
  This meeting is organized by the National Executive currently in office and takes place after CELC, where elections are held, and before Spring Meeting.
\end{enumerate}

