\section{CEC Appeal Process}\label{cec-appeal-process}

\subsection{Appeals on Changes that Impact More Than One CEC}\label{appeals-on-changes-that-impact-more-than-one-cec}

\begin{enumerate}
 \item
  All appeals that fit into this category must be made within two weeks of the decision by the CECAB.
 \item
  To begin the appeal process, a letter detailing the decision that is being appealed and the reason for the appeal must be submitted to the Chair of the CECAB who then must inform both the CECAB and the CFES Board.
 \item
  The CFES Board shall respond to the appeal within one week of the notice from the CECAB Chair.
 \item
  This type of appeal needs a minimum of 10 signatories on the letter from any region or at least 1 signatory from each region of the CFES.

  \begin{enumerate}
   \item
    The signatories to the letter must be the proxy holders from CFES members
  \end{enumerate}

 \item
  All decisions made by the CFES Board are final.
\end{enumerate}

\subsection{Appeals Impacting The Current CEC}\label{appeals-impacting-the-current-cec}

\begin{enumerate}
 \item
  All appeals that fit into this category must be made within one week of the conclusion of CEC.
 \item
  To begin the appeal process, a letter detailing the decision that is being appealed and the reason for the appeal must be submitted to the Chair of the CECAB who then must inform both the CECAB and the CFES Board.
 \item
  The CFES Board shall respond to the appeal within one week of the notice from the CECAB Chair.
 \item
  This type of appeal needs to have consensus from the majority of the team filing the appeal, noted by the signatures of 50\%+1 of the team members on the appeal letter.

  \begin{enumerate}
   \item
    The regional head delegate may sign the letter but their signature will not count towards the percentage needed to obtain majority consensus.
  \end{enumerate}

 \item
  All decisions made by the CFES Board are final.
\end{enumerate}
