\section{Awards}\label{awards}

\subsection{Purpose/Overview}\label{purposeoverview}

\begin{enumerate}
 \item
  At each CELC, the CFES presents awards to select individuals, groups, and Members in acknowledgement of their contributions to either the Federation or to the Canadian engineering community.
 \item
  All awards are to be presented at CELC, with the exception of the award noted in Section 9.3, which is to be presented at CESS.
\end{enumerate}

\begin{enumerate}
 \item
  The CFES encourages the Regional Ambassador and/or VPX of the award winners to plan an in-person ceremony after the presentation at CESS, as is feasible.

  \begin{enumerate}
   \item
    An awards committee is to be struck at the discretion of the President for both the CELC and CESS awards, and has the authority to grant all awards unless otherwise noted.
  \end{enumerate}
\end{enumerate}

\subsection{Awards Presented at CELC}\label{awards-presented-at-celc}

\subsubsection{Overview}\label{overview}

\begin{enumerate}
 \item
  The following awards are to be presented each year; additional awards may be presented on the basis of outstanding contributions or significant merit.
\end{enumerate}

\subsubsection{Appreciation Award}\label{appreciation-award}

\begin{enumerate}
 \item
  The CFES Appreciation Award recognizes significant contributions to the CFES from a non-student.
 \item
  The award is presented annually to a higher education institution staff or faculty member, someone from industry or from another organization.
\end{enumerate}

\subsubsection{Leadership Award}\label{leadership-award}

\begin{enumerate}
 \item
  The CFES Leadership Award recognizes significant contributions by an engineering student to enhance the image of the undergraduate engineering community in Canada.
 \item
  The award is presented annually to an engineering student who has, through various higher education institution and community endeavors, promoted the good of engineering students and the profession to society.
\end{enumerate}

\subsubsection{Charity Award}\label{charity-award}

\begin{enumerate}
 \item
  The CFES Charity Award recognizes significant charitable contributions.
 \item
  The award is presented annually to the member that has made outstanding contributions towards a charitable cause over the past year.
\end{enumerate}

\subsubsection{CFES Team Appreciation
 Award}\label{cfes-team-appreciation-award}

\begin{enumerate}
 \item
  The CFES Team Appreciation Award is chosen by the National Executive to recognize the contribution of a member of the CFES Team to the Federation.
\end{enumerate}

\subsubsection{Chair's Award}\label{chairs-award}

\begin{enumerate}
 \item
  This award is chosen by the Board Chair and is given to the representative of a member society who participated in the Annual General Meeting in an exceptional and enthusiastic fashion.
\end{enumerate}

\subsubsection{CFES Advocacy Award}\label{cfes-advocacy-award}

\begin{enumerate}
 \item
  Recognizes significant contributions by an engineering student to issues facing the community, either through identifying, researching, or advocating for awareness or change.
 \item
  The Advocacy Award could be awarded for support given to any of our stances.
\end{enumerate}

\subsubsection{Environmental Stewardship
 Award}\label{environmental-stewardship-award}

\begin{enumerate}
 \item
  Recognizes an engineering student who has either founded or made significant improvements to an environmental stewardship or protection initiative.
 \item
  The recipient of this award should be creating innovative solutions that minimize environmental impact and promote responsible resource management within the engineering field, aligning with the CFES' stance on sustainability.
\end{enumerate}

\subsection{Awards Presented at CESS}\label{awards-presented-at-cess}

\subsubsection{Activity Appreciation
 Award}\label{activity-appreciation-award}

\begin{enumerate}
 \item
  The CFES Activity Appreciation Award recognizes significant contributions from an Organizing Committee member or members of an activity from that academic year.
\end{enumerate}

