\section{Inclusive Conference
  Guidelines}\label{inclusive-conference-guidelines}

\subsection{Purpose}\label{purpose-3}

\begin{enumerate}
 \item
  To best serve our members, it is essential that the Federation's conferences and activities be safe spaces that encourage discussion and learning amongst its members.
 \item
  To this end, it shall be the policy of the Federation to facilitate the following:
\end{enumerate}

\begin{enumerate}
 \item
  A Conference Code of Conduct;
 \item
  An Incident Reporting System, with a Response Committee at each Activity;
 \item
  Inclusivity Orientation at CELC every year
 \item
  Provide Inclusive Conference Planning information to Activity Managers upon ratification
 \item
  Inclusion in pre-delegate packages of information on accessibility features available at the main venue(s) of any Activity.
 \item
  A Conference Expectations Debrief for all delegates before the conference
\end{enumerate}

\subsection{Conference Code of
 Conduct}\label{conference-code-of-conduct}

\begin{enumerate}
 \item
  The CFES Conference Code of Conduct shall be distributed at least one month before each Activity, and shall be as follows:
\end{enumerate}

\emph{The Canadian Federation of Engineering Students aims to promote
 inclusive and respectful environments where all students feel safe,
 welcome, and valued. To accomplish this, the CFES expects students to
 behave in an inclusive and respectful manner befitting a future
 engineer.}

\emph{By attending a CFES conference, you commit to:}

\begin{itemize}
 \item
  \emph{Value other people's experiences;}
 \item
  \emph{Embody a spirit of respect and fellowship;}
 \item
  \emph{Maintain respectful communication regardless of disagreements;}
 \item
  \emph{Have an open mind for new ideas and information;}
 \item
  \emph{Refrain from behaving in a manner that degrades, insults, or
   otherwise negatively affects others;}
 \item
  \emph{Support your peers; and}
 \item
  \emph{Grow and develop professionally, academically, and socially.}
 \item
  \emph{Respect other people's privacy and adhere to a respectful
   rooming etiquette.}
\end{itemize}

\emph{The CFES is based on the combined effort, dedication, and
 commitment of its students. Abiding by this Code of Conduct actively
 contributes to building a better CFES and promotes positive CFES
 environments.}

\emph{I,
 (Name)\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
 of
 (School)\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
 have read the CFES Conference Code of Conduct. I not only understand the
 Code, but also appreciate its importance to my personal experience and
 the experience of others. I agree to actively follow the Code for
 (conference)
 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_, and to
 encourage and support others in doing the same.}

\emph{Non-Head Delegates: Signed this day date\_\_\_\_\_\_\_\_\_\_\_with
 my head delegate \_\_\_\_\_\_\_\_\_\_\_\_\_\_as witness.}

\emph{Head Delegates \& CFES Team: Signed this day date
 \_\_\_\_\_\_\_\_\_\_\_\_with Board Member \_\_\_\_\_\_\_\_\_\_\_\_as}

\emph{witness.}

\emph{Observed violations of the Code of Conduct should be reported via
 the Incident Reporting System. Failure to follow the Code may result in
 consequences ranging from verbal reprimand to expulsion from the current
 and future CFES events. The attendee's academic institution may also be
 contacted.}

\subsection{Accessibility Information}\label{accessibility-information}

\subsubsection{Pre-Delegate Package
 Content}\label{pre-delegate-package-content}

\begin{enumerate}
 \item
  To ensure that potential delegates are aware in advance of any obstacles to their participation which may be present at a conference, pre-delegate packages for all activities will include information on the following:
\end{enumerate}

\begin{enumerate}
 \item
  The presence of accessible accommodations and obstacles for those with limited mobility
 \item
  Any restrictions on service animals which may exist at the Activity's main venue(s)
 \item
  The availability or lack of availability of food meeting the requirements of common dietary restrictions, including vegetarian, vegan, gluten-free, lactose-free, halal, and kosher options.
 \item
  The availability or lack of availability of translation resources such as define in Section 13.4.
 \item
  A list of the common words and official abbreviations with their meaning at conferences.
 \item
  Other information as determined by the relevant Activity Manager or the VP Services.
\end{enumerate}

\subsubsection{Conference
 Accountability}\label{conference-accountability}

\begin{enumerate}
 \item
  The VPS and OC of the conference must meet at least three times before the conference to ensure that Section 13.3 is fulfilled.
\end{enumerate}

\begin{enumerate}
 \item
  The first meeting is to happen at least 6 months before the conference.
 \item
  The second meeting is to happen at least 1 month before the pre-delegate package is sent.
 \item
  The third meeting is to happen at least 3 weeks before the conference start.

  \begin{enumerate}
   \item
    The VPS and OC of the respective conference must meet after the conference to discuss whether the accessibility expectations were fulfilled.
   \item
    The Board assigns a warning status to the host of the investigated conference if there is a lack of professionalism from the host and it is host's first time.
   \item
    The warning status is to be removed if the same host runs a successful conference.
   \item
    When the warned host plans another conference with the warning status is still being held and the conference still has a problem, the Board is to place the member school in bad standing.
   \item
    In case the report displayed a lack of planning from the OC of the respective conference, the membership can mandate the Board to perform an investigation.
   \item
    The Board is to share the findings and results of the investigation with the member schools within a month after the investigated member school is being notified of the results.
  \end{enumerate}
\end{enumerate}

\subsection{Translation Service
 Guidelines}\label{translation-service-guidelines}

\begin{enumerate}
 \item
  The following items are the possible resources that can be available at conferences:
\end{enumerate}

\begin{enumerate}
 \item
  Bilingual PowerPoint, signs and documents made for the conference
 \item
  Bilingual presenter
 \item
  Simultaneous translation : subtitles, bilingual volunteers/delegate with unilingual presenter
 \item
  Translated script
 \item
  Translated session minutes
 \item
  Cards with common words distributed to delegates
 \item
  Providing resources or immersive training to key members/CFES Team : teaching basic vocabulary, relevant words and key terms
 \item
  Easily identifiable bilingualism delegate
\end{enumerate}

