\section{Commissioner Travel Fund for Conferences with General Assemblies}\label{commissioner-travel-fund-for-conferences-with-general-assemblies}

\subsection{Overview}\label{overview-4}

\begin{enumerate}
 \item
  This travel fund only applies to Conferences with General Assemblies, for other CFES meetings such as Spring, Summer, and Fall meetings, Commissioners will apply to the normal Board Member Travel Fund.
 \item
  The amount in this Fund is only the amount that has been reallocated after the finalization of the Member School funding Travel Fund allocation.
\end{enumerate}

\subsection{Deadlines}\label{deadlines}

\begin{enumerate}
 \item
  The Commissioner Travel Fund will open as soon as the Member School funding Travel Fund allocation is finalized and the resulting allocation is announced.
 \item
  The application will be open for 5 days.
 \item
  A Board Meeting will be held within 48 hours of the closing of the application.
 \item
  A decision will be rendered by the Board at the aforementioned Board Meeting, and the results of the allocation of funds will be made available to all applicants at least 48 hours before the end of pre-registration.
\end{enumerate}

\subsection{Special Circumstances}\label{special-circumstances}

\begin{enumerate}
 \item
  In the event that there is no pre-registration for a conference with a GA, this will be considered a special circumstance.
 \item
  In these special circumstances, the deadline relating to the announcement of the results of the allocation detailed in Section 14.2.4 will be superseded and the application process will instead follow the following timeline.
 \item
  The Board Meeting must be scheduled within 48 hours of the closing of the application.
 \item
  A decision will be rendered by the Board at the aforementioned Board Meeting, and the results of the allocation of funds will be made available to all active members as soon as possible.
 \item
  The results of the allocation must be sent to all applicants at least 48 hours before the end of the conference registration.
\end{enumerate}

\subsection{Selection Process}\label{selection-process}

\begin{enumerate}
 \item
  The Vice President Finance and Administration will review all applications submitted and submit recommendations of funding to the Board for allocation.
 \item
  The application will require the following information from an applicant Commissioner:

  \begin{enumerate}
   \item
    Statement of intent explaining why the applicant is unable to finance their attendance at Summit on Development of Engineering Societies or CELC, and further explaining how there will be mutual benefit from attending Summit on Development of Engineering Societies or CELC to both the applicant and CFES
   \item
    Amount requested and expected cost
   \item
    Planned method of travel
   \item
    List of conferences the applicant has attended and/or intends to attend in the period between the Summit on Development of Engineering Societies or CELC the application is for, and of the previous fiscal year.
   \item
    Detailed explanation of how the applicant has attempted to raise the amount being requested from their Dean, alumni and other available sources.
  \end{enumerate}

\end{enumerate}
