\section{Information Technology
  Security}\label{information-technology-security}

\begin{enumerate}
 \item
  All officials of the CFES shall abide by the following policies while using electronic services provided by the CFES or electronic services being used for official CFES purposes.
 \item
  Official CFES emails or a suitable alternative determined by the IT Commissioner shall be used for all communications.
 \item
  Any domain name that is affiliated with the CFES or any CFES groups will be properly registered to the CFES
 \item
  When a CFES official leaves their CFES position, all account passwords shall be reset within 48 hours.
 \item
  The IT Commissioner must be able to reset any password associated with an account used for official purposes.
 \item
  Any data which is created, stored, transferred, broadcasted, or hosted on a server or computer which is owned by the CFES or is under the purview of the IT Commissioner must be adhere to the policies specified in the Information Handling and Security Policy regarding the transfer and storage of classified documents if applicable.
 \item
  Strong passwords shall be used for all accounts.
\end{enumerate}

\begin{enumerate}
 \item
  A strong password is one is at least 8 characters and contains at least one of each of the following: uppercase letters, lowercase letters, number, special character.
 \item
  Exceptions can be made upon approval from the IT Commissioner; these requests shall never divulge the exact password but simply describe the format of the password and why it cannot meet the specified requirements.

  \begin{enumerate}
   \item
    Classified documents or otherwise private documents shall be stored in either a cloud storage system approved by the IT Commissioner or in an encrypted storage medium.
  \end{enumerate}
\end{enumerate}

\begin{enumerate}
 \item
  These documents may only be accessible by officials that require the information in these documents.
 \item
  These documents shall not be stored on personal media including but not limited to laptop hard disks, non-approved cloud storage, or un-encrypted personal removable storage.

  \begin{enumerate}
   \item
    The Information Technology Commissioner shall perform penetration testing on the CFES electronic infrastructure at a minimum of once per quarter.
  \end{enumerate}
\end{enumerate}

