\section{Digital Platforms \&
  Services}\label{digital-platforms-services}

\subsection{Overview}\label{overview-5}

\begin{enumerate}
 \item
  The National Executive may employ the use of digital platforms that support the operations of the Federation.
 \item
  All digital platforms and services that require a monthly or annual subscription must be approved by the Board.

  \begin{enumerate}
   \item
    Activity Managers are exempt of this requirement for platforms acquired for their respective Activity
  \end{enumerate}
\end{enumerate}

\subsection{Google Workspace}\label{google-workspace}

\begin{enumerate}
 \item
  The Federation utilizes Google Workspace as the central production and collaboration tool, including meetings, e-mail, and file sharing.
 \item
  The following positions should be granted Super Administrator privileges:
\end{enumerate}

\begin{enumerate}
 \item
  President
 \item
  Vice President Communications
 \item
  Vice President Finance \& Administration
 \item
  Information Technology Commissioner
\end{enumerate}

\subsection{Flickr}\label{flickr}

\begin{enumerate}
 \item
  The Federation utilizes Flickr as the central image hosting platform for CFES events and activities.
 \item
  The Vice President Communications is responsible for the upkeep and management of this platform.
\end{enumerate}

\subsection{Squarespace}\label{squarespace}

\begin{enumerate}
 \item
  The Federation utilizes Squarespace as its website hosting and content management platform.
 \item
  The Vice President Communications shall be responsible for the upkeep and management of this platform.
\end{enumerate}

\subsection{Domains}\label{domains}

\begin{enumerate}
 \item
  The Federations utilizes the following website domains:
\end{enumerate}

\begin{enumerate}
 \item
  cfes-fceg.ca

  \begin{enumerate}
   \item
    This shall serve as the primary website address for the Federation.
   \item
    This domain will be designated as a user alias domain for cfes.ca within Google Workspace
  \end{enumerate}
 \item
  cfes.ca

  \begin{enumerate}
   \item
    The shall serve as the primary domain for Google Workspace and all email accounts.
   \item
    This website address shall redirect to cfes-fceg.ca
  \end{enumerate}
 \item
  fceg.ca

  \begin{enumerate}
   \item
    This website address shall redirect to cfes-fceg.ca
   \item
    This domain shall be designated as a user alias domain for cfes.ca within Google Workspace
  \end{enumerate}
\end{enumerate}

