\section{Article 3 - Membership}
\label{article-3---membership}

\subsection{Member Societies}
\label{member-societies}

\subsubsection{Structure}
\label{member-structure}
\begin{enumerate}
 \item Member Societies, also referred to as “Members” and “the Membership”, are Engineering Societies, as defined in the Terms \& Definitions of this Constitution.
 \item A Member Society pays annual membership fees, as determined in the Policy Manual.
 \item A Member Society has the right to one vote at General Meetings of the Federation.
\end{enumerate}

\subsubsection{Regular Member}
\label{regular-member-engineering-society}

\begin{enumerate}
 \item A Regular Member of the Federation is a Member Society which has received the support of the Membership as specified in Article 3.2.
\end{enumerate}

\subsubsection{Cooperative Regular Member}
\label{cooperative-regular-member}

\begin{enumerate}
 \item Multiple Engineering Societies may apply to co-represent the undergraduate engineering students at their institution as if eligible to be a Regular Member as defined in Article 3.1.4 where there is no single society fitting the description.
 \item A Cooperative Regular Member is identical to a Regular Member in all ways except the voting representative must be confirmed by each cooperative society President.
\end{enumerate}

\subsection{Application for Membership}
\label{application-for-membership}

\begin{enumerate}
 \item To become a Member Society an organization must submit a written application to the Vice-President Finance and Administration, who must immediately inform the Members of such an application.
 \item The Members must then make a decision regarding the organization admission, and no later than the General Meeting following the organisation's submission of the application.
\end{enumerate}

\subsection{Observer Status}
\label{observer-status-engineering-society}

\begin{enumerate}
 \item An Observer of the Federation is an Engineering Society which received the support of the Board as specified in the Bylaws.
 \item Observer status is valid for one year after an application is approved after which point the Observer must choose to apply to become a Regular Member as per Article 3.1.2, apply for a one-time extension or withdraw membership both as per the Bylaws.
\end{enumerate}
