\section{Article 13 - Financial and Legal Dispositions}
\label{article-13---financial-and-legal-dispositions}

\subsection{External Audit}
\label{external-audit}

\subsubsection{The Federation}
\label{the-federation-audit}

\begin{enumerate}
 \item The Federation must conduct an external audit annually.
 \item The auditing entity is to be approved annually at the annual general meeting.
 \item The cost of this financial review is to be estimated at the time of their approval, the total cost incurred shall be reported at every meeting of the membership.
\end{enumerate}

\subsubsection{Activities}
\label{activities}

\begin{enumerate}
 \item All CFES Activities must undergo an external audit, done through the organization that handled the financial accounts for the Activity.
 \item This will be either the CFES or an incorporated body as approved by the Board.
 \item The CFES Audit Costs, outlined in Article 13.1.3, will only apply to host schools that use CFES bank accounts for their Activity.
\end{enumerate}

\subsection{Audit by Membership}
\label{audit-by-membership}

\begin{enumerate}
 \item At the Summit on Development of Engineering Societies, an active member may request to audit the books of the Federation for the current year.
 \item The member must report to the next Annual General Assembly.
 \item If more than one member makes a request, the General Assembly, or the Board, appoint the member responsible for the audit.
\end{enumerate}

\subsection{Reimbursements}
\label{reimbursements}

\subsubsection{Ordinary}
\label{ordinary}

\begin{enumerate}
 \item Board Members will be reimbursed of all costs, charges and expenses they sustain or incur in or about any action, suit or proceedings which is brought, commenced or prosecuted against them, or in respect of any act, deed, matter or thing whatsoever, made, done or permitted by them, in or about the execution of the duties of this office or in respect of any such liability.
\end{enumerate}

\subsubsection{Extraordinary}
\label{extraordinary}

\begin{enumerate}
 \item The Board may authorize the reimbursement of Board Members of all other costs, charges and expenses which they sustain or incur in or about or in relation to the affairs thereof, except such costs, charges or expenses as are occasioned by their own wilful neglect or default.
\end{enumerate}

\subsection{Trust Company}
\label{trust-company}

\begin{enumerate}
 \item The Board shall have power to authorize expenditures on behalf of the Federation from time to time and may delegate by resolution to a Board Member the right to employ and pay salaries to employees.
 \item The Board shall have the power to enter into a trust arrangement with a trust company for the purpose of creating a trust fund in which the capital and interest may be made available for the benefit of promoting the interest of the Federation in accordance with such terms as the Board or members may prescribe.
\end{enumerate}

\subsection{Donations}
\label{donations}

\begin{enumerate}
 \item The Board shall take such steps as they may deem requisite to enable the Federation to acquire, accept, solicit or receive legacies, gifts, grants, settlements, bequests, endowments and donations of any kind whatsoever for the purpose of furthering the objectives of the Federation.
\end{enumerate}

\subsection{Power of Attorney}
\label{power-of-attorney}

\begin{enumerate}
 \item The Board may give the Federation power of attorney to any registered dealer in securities for the purposes of the transferring of and dealing with any stocks, bonds, and other securities of the Federation.
\end{enumerate}

\subsection{Contracts}
\label{contracts}

\subsubsection{Signing Requirements}
\label{signing-requirements}

\begin{enumerate}
 \item Any contracts, documents or any instruments in writing shall be signed by the Vice President Finance and administration.
 \item All contracts so signed shall be binding upon the federation without any further authorization or formality if the value does not exceed \$1000.
 \item Contracts, documents or any instruments in writing exceeding \$1000 requiring the signature of the Federation, shall be signed by any two members of the National Executive.
 \item All contracts, documents and instruments in writing so signed shall be binding upon the Federation without any further authorization or formality if the value does not exceed \$10,000.
 \item For a contract with a value in excess of \$10,000, a resolution authorizing its signing must be adopted by the Board.
 \item Any contracts, documents or any instruments in writing requiring the signature of the Federation for an activity or a service shall be signed by its Activity Manager, or their delegate, also requiring the approval of the Board if in excess of \$10,000.
\end{enumerate}

\subsubsection{Special Signing Officer}
\label{special-signing-officer}

\begin{enumerate}
 \item The Board shall have power from time to time by resolution to appoint a member of the CFES Team of the Federation to sign specific contracts, documents and instruments in writing.
\end{enumerate}
